Copy number inference with InferCNV

### 2024-05-29 analyses/cell-type-ewings/template_notebooks/04-infercnv.Rmd

---
title: "Copy number inference with InferCNV"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "../results/annotate_tumor_cells_output/SCPCS000490/SCPCL000822_tumor-normal-classifications.tsv"
  infercnv_dir: "../results/annotate_tumor_cells_output/SCPCS000490/infercnv"
  results_dir: "../results/annotate_tumor_cells_output/SCPCS000490"
---

>>>>

---
title: "Copy number inference with InferCNV"
author: Ally Hawkins
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_depth: 3
params:
  sample_id: SCPCS000490
  library_id: SCPCL000822
  marker_gene_classification: "tumor-normal-classifications.tsv"
  infercnv_dir: "infercnv"
  results_dir: "annotate_tumor_cells_output"
---
